GSS Education Analysis (Working Title)

### 2023-03-14 outputs/paper/paper.qmd
add table of contents and label some sections

---
title: "GSS Education Analysis (Working Title)"
subtitle: "GSS Education Analysis (Working Subtitle)"
author: 
  - Emily Kim
  - Huda Sahaf
  - Chloe Thierstein
thanks: "Code and data are available at: https://github.com/cthierst/gss_education_analysis.git"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "abstract (work in progress)"
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Introduction

@@

@@

# Results

@@

## First discussion point {#sec-first-point}

@@

# Appendix {.unnumbered}

# Additional details

>>>>

---
title: "GSS Education Analysis (Working Title)"
subtitle: "GSS Education Analysis (Working Subtitle)"
author: 
  - Emily Kim
  - Huda Sahaf
  - Chloe Thierstein
thanks: "Code and data are available at: https://github.com/cthierst/gss_education_analysis.git"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "abstract (work in progress)"
format: pdf
toc: TRUE
number-sections: TRUE
bibliography: references.bib
---

@@

# Introduction {#sec-introduction}

@@

## Data Management {#sec-first-point}

## Source and Methodology

## Sampling

## Weighting

## Key Features

@@

# Results {#sec-results}

@@

## First discussion point

@@

# Appendix
